---
title: "Staygreen Trait Efficacy"
author: "Nilesh Dighe"
date: "April 20, 2015"
output: html_document
---
###Year of data collection: 2012
###Moisture stress levels:  Mod-High
###Locations: Three
  + *Hale Center, TX*
  + *Levelland, TX*
  + *Lamesa, TX*
```{r, include=FALSE}
library(caret)
library(ggplot2)
library(agricolae)
library(dplyr)
library(Hmisc)
library(gridExtra)
```

```{r,echo=FALSE}
efficacy2012<- read.csv("2012_STGvalid.csv", head=T)
efficacy2012$Rep<- as.factor(efficacy2012$Rep)
```
*create subset by only including the experimental lines from bi-parental crosses*
```{r}
High<- filter(efficacy2012, StaygreenGroup=="High-STG")
Mod<- filter(efficacy2012, StaygreenGroup=="Mod-STG")
Non<- filter(efficacy2012, StaygreenGroup=="Non-STG")
df<- data.frame()
pops<- rbind(df, High, Mod, Non)
#str(pops)
#head(pops)
#tail(pops)
```

*Cut Staygreen phenotype using the average Staygreen phenotype across all reps. Cut is made by dividing AvgSTG into three quantile groups*
```{r}
cutAvgSTG<- cut2(pops$AvgSTG,g=3)
table(cutAvgSTG)
```

*Staygreen groups compared for YLDBE using box plots*
```{r}
p1<- qplot(cutAvgSTG, YLDBE, data=pops, fill=StaygreenGroup, geom=c("boxplot"),na.rm=TRUE)
p2<- qplot(cutAvgSTG, YLDBE, data=pops, fill=StaygreenGroup, geom=c("boxplot","jitter"),na.rm=TRUE)
grid.arrange(p1,p2,ncol=2)
```
*Staygreen groups compared for YLDBE using density plot*
```{r, warning=FALSE}
qplot(YLDBE, colour=StaygreenGroup,data=pops,geom="density")
```
*Scatterplots comparing Staygreen phenotype to YLDBE*
```{r, warning=FALSE}
#scatterplot without fitted line but colored by decision
scatter3<- qplot(STG,YLDBE, data=pops, color=StaygreenGroup)
scatter3 + geom_point() + facet_wrap(~ Origin, as.table=FALSE) + scale_color_manual(values = c("Mod-STG"="orange","Non-STG"="red", "High-STG"="dark green"))
#scatterplot with fitted line but no color
scatter2<- qplot(STG,YLDBE, data=pops)
scatter2 + geom_point() +  geom_smooth(method=lm) + facet_wrap(~ Origin, as.table=FALSE)
#scatterplot with fitted line BUT no facet wraps
scatter5<- qplot(STG,YLDBE, data=pops)
scatter5 + geom_point() +  geom_smooth(method=lm)
```
*Yield distributions for the three Staygreen groups by and across Origins*
```{r,warning=FALSE,message=FALSE}
#trait distribution and bar plotting using facet_wrap
g<-  qplot(YLDBE, data=pops, fill=StaygreenGroup)
g + geom_bar() + facet_wrap(~ Origin, as.table=FALSE) + scale_fill_manual(values = c("Mod-STG"="orange","Non-STG"="red", "High-STG"="dark green"))
#trait distribution and bar plotting without facet_wrap
g<-  qplot(YLDBE, data=pops, fill=StaygreenGroup)
g + geom_bar() + scale_fill_manual(values = c("Mod-STG"="orange","Non-STG"="red", "High-STG"="dark green"))
```

